%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=0.5cm,right=6.5cm,marginparwidth=5.8cm,marginparsep=0.2cm,top=0.5cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{444444}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{Raudel Alejandro Gómez Molina}
\tagline{Computer Scientist}
% \photo{2.8cm}{Globe_High}
\personalinfo{%
	% Not all of these are required!
	% You can add your own with \printinfo{symbol}{detail}
	\email{raudel.gmolina@gmail.com}
	\phone{(+53) 59253662}
	%  \mailaddress{Address, Street, 00000 County}
	\location{Havana, Cuba}
	\linkedin{raudel25}
	\github{raudel25}
	\homepage{https://raudel25-portfolio.vercel.app}
	%  \twitter{@marissamayer}
	%   \linkedin{jatin-varlyani}
	%   \github{Jatin-8898} % I'm just making this up though.
	%% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
	%   \orcid{orcid.org/0000-0000-0000-0000}
}





%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
	\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Full stack developer}{jobs2live}{Sep 2023 -- Jan 2024}{Madrid, Spain}
\begin{itemize}
	\item TypeScript, React, Antd, C\#, .Net, MySQL, Odata
	\item I was part of the construction of the company's platform, participating in the modeling and structuring of the website.
	\item Database model with MySQL and react components using Andt.
	\item \href{https://www.jobs2live.com/website}{jobs2live web site}.
	      
\end{itemize}

\divider

\cvevent{Mobile developer}{Business Seed}{Feb 2024 -- Present}{Mexico DF, Mexico}
\begin{itemize}
	\item Dart, Flutter, Getx
	\item I worked creating hybrid applications for Android and iOS.
	\item Push notification, location, google maps, camera,
	      scan qr, local controllers for android client of the recolector machine. 
	\item Application creation from strach and integration with API-REST to achieve MVP in a short time.
	\item In the design of applications, Clean Architecture is used, using design patterns and SOLID principles.
	\item \href{https://land.mideyneutraliza.com/}{User app for Loop project},
	      \href{https://land.mideyneutraliza.com/}{Recolector app for Loop project}, \href{https://land.mideyneutraliza.com/}{Machine app for Loop project}, Delivery app for El navegate project.
	      
\end{itemize}

\divider

\cvevent{Mobile Developer}{Bizne MX}{May 2024 -- Present}{Mexico DF, Mexico}

\begin{itemize}

	\item Dart, Flutter, Getx
	\item I worked creating hybrid applications for Bizne platform.
	\item Push notification, location, google map, camera service,
	      scan qr. 
	\item Creation and maintenance of the new version of the Bizne application built in Flutter.
	\item \href{https://play.google.com/store/apps/details?id=mx.devbizne.bizne&hl=en-US}{User app for Bizne project},
	      \href{https://play.google.com/store/apps/details?id=mx.bizne.kitchen&hl=en-US}{POS app for Bizne project}.
\end{itemize}

\divider

\cvevent{AssistantProfessor}{Havana University}{Apr 2022 -- Present}{Havana, Cuba}

\begin{itemize}

	\item Competitive Programming, Data Structures and Algorithms.
	\item  During my studies at the university I have worked as anassistant in the subjects of Algebraand Data Structures and Algorithms.
	      
	      
\end{itemize}

\cvsection{Skills}
\cvtag{React}
\cvtag{Next}
\cvtag{JavaScript}
\cvtag{TypeScript}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{C/C++}
\cvtag{C\#}
\cvtag{.Net}
\cvtag{MySQL}
\cvtag{PostgreSQL}
\cvtag{Docker}
\cvtag{Python}
\cvtag{Git}
\cvtag{Github}
\cvtag{Dart}
\cvtag{Flutter}
\cvtag{Getx}
\cvtag{Go}
\cvtag{Rust}

\clearpage

%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the 
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}